---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Libraries

```{r}
library(tidyverse)
library(brms)
library(haven)
```

# Making Datasets ready for cleaning and analysis.

## Merge Household and Individual Level Data for NLFS 1.

```{r} 
# Read the dataset.

nlfs1_h <- read_dta("Data/nlfs1_household.dta")
nlfs1_i <- read_dta("Data/nlfs1_individual.dta")

# Merge 1:m using psuhhno (PSU and household number). The resulting dataset must ideally have 67,088 observations.

nlfs1_i_m <- left_join(nlfs1_i, nlfs1_h, by = c("psuhhno"))
d1 <- nlfs1_i_m
```

## Merge Household and Individual Level Data for NLFS 2

```{r}
# Read the dataset.

nlfs2_h <- read_dta("Data/nlfs2_household.dta")
nlfs2_i <- read_dta("Data/nlfs2_individual.dta")

# Merge the datasets such that there are ideally 76,028 observations from the individual dataset.

nlfs2_i_m <- left_join(nlfs2_i, nlfs2_h, by = c("psu", "hhid"))
d2 <- nlfs2_i_m
```

# Clean Datasets.

## Clean and make NLFS 1 dataset ready for analysis:

### Renaming some important variables.

```{r}
d1 <- d1 %>% rename(
  sex = q01,
  age = q02,
  hhsize = tothhmem.x,
  marital_status = q04,
  ethnicity = ethnicty.x,
)

# Note: var.x and var.y in this context are the same. R just likes to keep both during merge if the column name is the same.

# One can check this using all.equal(d1$ethnicty.x, d1$ethnicty.y)
```


### Create overall household variables.

```{r}
d1 <- d1 %>% mutate(
  # 1 is married, 0 is everything else
  marital_status = ifelse(marital_status !=2 | is.na(marital_status),
                          0, 1), 
  sex = if_else(sex == 2, 0, 1), # 1 is male
  nlfs_year = 1998,
  urbrur = if_else(urbrural.x %in% c(1, 2), 1, 0 ), # 1 is urban
  perma_resident = NA,
  district_name = as.character(as_factor(district.x)),
  district_abbrev = str_sub(str_to_lower(district_name), 1, 4),
  hindu = if_else(religion.x == 1, 1, 0),
  brahmin_chhetri = if_else(ethnicity %in% c(1, 2), 1, 0)
)

# filter those whose age is less than 10.
```

### Work Hours related variables.

```{r}
# Wage Hours.

d1 <- d1 %>% mutate(
  # Note Not Applicable Values are NA for now.
  wage_hours = ifelse(q16a > 84, 84, q16a),
)

# Self Employment Hours
d1 <- d1 %>% mutate(
  rs_selfemp = rowSums(select(., q16b:q16i), na.rm =T),
  selfemp_hours = if_else(rs_selfemp > 84, 84, rs_selfemp)
)

# Self Employment Hours (outside)
d1 <- d1 %>% mutate(
    rs_selfemp_o = rowSums(select(., q16b:q16f), na.rm =T),
    selfemp_hours_outside = if_else(rs_selfemp_o > 84, 84, rs_selfemp_o)
)

# Work Hours (overall, inside, and outside)

d1 <- d1 %>% mutate(
  rs_workhours = rowSums(select(., q16a:q16i), na.rm =T),
  rs_workhours_o = rowSums(select(., q16a:q16f), na.rm =T),
  rs_workhours_i = rowSums(select(., q16g:q16i), na.rm =T),
  
  
  work_hours = if_else(rs_workhours > 84, 84, rs_workhours),
  work_hours_outside = if_else(rs_workhours_o > 84, 84, rs_workhours_o),
  work_hours_inside = if_else(rs_workhours_i > 84, 84, rs_workhours_i)
)


# Non Work Hours
d1 <- d1 %>% mutate(
  nonwork_hours = rowSums(select(., q17a:q17g), na.rm = T)
)

# Total Hours (both outside `Work` as well as inside stuff.)

d1 <- d1 %>% mutate(
  rs_total = rowSums(select(., work_hours, nonwork_hours), na.rm = T),
  total_hours = if_else(rs_total > 110, 110, rs_total)
)
```


### Employed and Unemployed Status related variables.

```{r}
d1 <- d1 %>% mutate(
  # Some 9000 values are NA which includes children under 5
  currently_emp = ifelse(
    work_hours !=0 | (q18 == 1 & (q19 == 1 | q20 == 1)),
    1, 0
  ),
  # Some 10,000 values are NA which includes children under 10
  currently_emp_out = ifelse(
    work_hours_outside !=0 | (q18 == 1 & (q19 == 1 | q20 == 1)),
    1, 0
  ),
  
  # Missing values are children
  currently_selfemp_out = ifelse(
    selfemp_hours_outside !=0 | (q18 == 1 & (q19 == 1 | q20 == 1)),
    1, 0
  ),
  
  # NAs are people who have not pursued wage jobs. 
  currently_emp_wage = ifelse(
    wage_hours !=0 | (q18 == 1 & (q19 == 1 | q20 == 1)),
    1, 0
  ),
  
  # Think of the NAs for these 
  currently_unemp = ifelse(
    q46 == 1 | (q46 == 2 & q51 !=5),
    1, 0
  ),
  
  currently_underemp = ifelse(
    q16 < 40 & (q37 %in% c(1:6)),
    1, 0
  ),
  
  currently_active = ifelse(
    currently_emp == 1 | currently_unemp == 1, 
    1, 0
  ),
  
  # If NA in currently active, then they are considered currently inactive
  currently_inactive = ifelse(
    currently_active != 1 | is.na(currently_active), 1, 0
  )
)
```

### Usually Active Statuses:

```{r}
d1 <- d1 %>% mutate(
  # Again, the NAs are children under the age of 5
  usually_active = ifelse(
    q58 >=180, 1, 0
  ),
  
  # Again, the NAs are children aged 5 or less.
  usually_inactive = ifelse(
    usually_active == 1, 0, 1
  ),
  
  usually_emp = ifelse(
    usually_active == 1 & (q54 > q55),
    1, 0
  ),
  
  usually_unemp = ifelse(
    usually_active == 1 & (q55 >= q54), 
    1, 0
  )
)
```

### Educational Metrics:

```{r}
d1 <- d1 %>% mutate(
  can_read = ifelse(q08 == 1, 1, 0),
  can_write = ifelse(q09 == 1, 1, 0),
  current_attend = ifelse(q10 == 1, 1, 0), 
  ever_attend = ifelse(q11 == 1, 1, 0),
  edu_others = ifelse(q12 == 16, 1, 0),
  ever_school = ifelse(q10 == 1 | q11 == 1, 1, 0),
  
  # This metric is only applicable for those who have ever attended school.
  years_of_edu  = case_when(
    q12 %in% c(16, 99) ~ NA,
    q12 == 13 ~ 16,
    q12 %in% c(14, 15) ~ 18,
    TRUE ~ q12
  ),
  
  # Those who have never attended school will be classified as 0.
  years_of_edu_all = ifelse(ever_school == 0, 0, years_of_edu)
  
)
```


## Select All the variables that are needed:

```{r}
d1_select <- d1 %>% select(nlfs_year, psu, age, hhsize, urbrur,
                           marital_status, hindu, brahmin_chhetri,
                           district_name, district_abbrev, 
                           wage_hours, selfemp_hours, selfemp_hours_outside,
                           work_hours, work_hours_outside, nonwork_hours, total_hours,
                           currently_emp, currently_emp_out, 
                           currently_selfemp_out, currently_emp_wage,
                           currently_unemp, currently_underemp, usually_emp, 
                           usually_unemp, currently_active, currently_inactive,
                           usually_active, usually_inactive, 
                           can_read, can_write, current_attend, 
                           ever_attend, years_of_edu, ever_school, years_of_edu_all
                           )

write_csv(d1_select, "Data/nlfs1_kept_individual.csv" )
```


## Clean NLFS 2 and make it ready for analysis.


### Overall Household Variables:
```{r}


d2 <- d2 %>% rename(
  age = q10,
  hhsize = totmemb,
)

d2 <- d2 %>% mutate(
  urbrur = ifelse(urbrur == 2, 0, 1), # urban is 1 and rural is 0
)

d2 <- d2 %>% mutate(
  nlfs_year = 2008,
  sex = ifelse(q09 == 2, 0, 1), # male is 1. 
  marital_status = ifelse(q13 == 2, 1, 0), # If married then 1, everything else 0
  hindu = ifelse(religion == 1, 1, 0),
  brahmin_chhetri = ifelse(q11 %in% c(1, 2), 1, 0),
  district_name = as.character(as_factor(dist)),
  district_abbrev = str_sub(str_to_lower(district_name), 1, 4)
)

# On permanent residency.

d2 <- d2 %>% mutate(
    not_perma_resident = ifelse(
      (q17 ==2 & q21 == 2 & q24 < 12) | (q17 == 1 & q21 == 2 & q24 < 12),
      1, 0
    ),
    # Some people probably did not answer question number 17.
    # Around 1520 people have NA values.
    # It seems to be the case that these people are not counted as household members. 
    perma_resident = ifelse(not_perma_resident == 1, 0, 1)
)
```

### Work Hours related variables:

```{r}
d2 <- d2 %>% mutate(
  # Wage Hours
  rs_wagehours = rowSums(select(., q36a:q36b), na.rm =T),
  wage_hours = ifelse(rs_wagehours > 84, 84, rs_wagehours),
  
  # Self Employment Hours (Total)
  rs_selfemp = rowSums(select(., q36c:q36j), na.rm = T),
  selfemp_hours = ifelse(rs_selfemp > 84, 84, rs_selfemp),
  
  # Self Employment Hours (Outside)
  rs_selfemp_o = rowSums(select(., q36c:q36g), na.rm = T),
  selfemp_hours_outside = ifelse(rs_selfemp_o > 84, 84, rs_selfemp_o),
  
  # Total Work Hours
  rs_workhours = rowSums(select(., q36a:q36j), na.rm = T),
  work_hours = ifelse(rs_workhours > 84, 84, rs_workhours),
  
  # Work Hours Outside
  rs_workhours_o = rowSums(select(., q36a:q36g), na.rm = T),
  work_hours_outside = ifelse(rs_workhours_o > 84, 84, rs_workhours_o),
  
  # Work Hours Inside (includes fetching water, collecting firewood,
  # and other home-based work activities. )
  rs_workhours_i = rowSums(select(., q36h:q36j), na.rm = T),
  work_hours_inside = ifelse(rs_workhours_i > 84, 84, rs_workhours_i)
)
```

### Employed and Unemployed Statuses:

```{r}
d2 <- d2 %>% mutate(
  # 9721 NAs and out of them 1200 are over the age of 5.
  currently_emp = ifelse(
    (work_hours > 0  | (q38 == 1 & (q39 == 1  | q40 == 1))),
    1, 0
  ),
  
  #11102 NAs but most of them under the age of 5 (exactly 8251 of them )
  currently_emp_out = ifelse(
    (work_hours_outside > 0  | (q38 == 1 & (q39 == 1  | q40 == 1))),
    1, 0
  ),
  
  #17,424 NAs, of which 8251 are children under 5
  currently_selfemp_out = ifelse(
    (selfemp_hours_outside > 0  | (q38 == 1 & (q39 == 1  | q40 == 1))),
    1, 0
  ),
  
  # 41,732 NAs : The reason probably is that there are not a lot wage workers
  # and how R deals with logical NAs. May have to fix it up later after filtering for age. 
  currently_emp_wage = ifelse(
    (wage_hours > 0  | (q38 == 1 & (q39 == 1  | q40 == 1))), 
    1, 0
  ),
  
  # Think of the NAs for these, there are currently a lot of NAs. It has
  # probably got sth to do with the fact of how R handles logical NAs. 
  # For a lot of the people, question number 77 is Not applicable, who in
  # reality must be casted as 0. 
  currently_unemp = ifelse(
    (q77 == 1 | (q77 == 2 & q82 != 5)),
    1, 0
  ),
  
  # No NAs here:
  currently_underemp = ifelse(
    work_hours < 40 & q68 %in% c(1:6),
    1, 0
  ),
  
  # 34,101 probably come from currently_unemp
  currently_active = ifelse(
    currently_emp == 1 | currently_unemp == 1,
    1, 0
  ),
  
  # NAs here probably should refer to currently_inactive. 
  currently_inactive = ifelse(
    currently_active == 1, 0, 1
  )
)

```


### Usually Active Status Variables. 

```{r}
d2 <- d2 %>% mutate(
  usually_active = ifelse(
    # 1 if people worked for all 12 months or if not, active months greater
    # than inactive months.
    
    # 9721 NAs out of which 8521 are children.
    (q88 >= q87) | (q85 == 12),
    1, 0
  ),
  
  usually_inactive = ifelse(
    usually_active == 1,
    1, 0
  ),
  
  # same 9721 NAs.
  usually_emp = ifelse(
    (usually_active == 1 & (q85 == 12 | q85>q86)),
    1, 0
  ),
  
  # same 9721 NAs. 
  usually_unemp = ifelse(
    (usually_active == 1 & (q85 !=12 & q86 >= q85)),
    1, 0
  )
)
```

